Individual heterogeneity in functional topography of the default-mode network in medial prefrontal cortex

### 2019-03-29 Manuscript.Rmd
updated the table

### *Table 1. Regions of interest from Glasser et al. (2016). Prefixes indicate hemispheric location (e.g. R = right).*
| Literature           | Significant Brain Regions                 |
| :------------------- | ----------------------------------------: |
| ROIs                 | `r str_remove(Yeo_labels, "_ROI")` |

>>>>

``` {r Subdivide search space into hemi-region for table, echo = FALSE, message = FALSE} 
# based on a subject's data, create a region vector for PCC and mPFC
# then split by region and hemisphere into a list (length = 4), and retain the unique (and stripped) labels for display
searchSpace <- Summaries[[1]] %>%
                  mutate(region = ifelse(y < 0, "PCC", "mPFC"),
                         Label = str_remove(substr(Label, 3, 20), "_ROI")) %>%
                  select(Hemisphere, region, Label) %>% # unneeded, but makes it easier to examine the df
                  split(list(.$Hemisphere, .$region)) %>%
                  lapply(., function(x) {unique(x$Label)})

### *Table 1. Parcels from Glasser et al. (2016) contained in the search space.*
| Hemisphere  |            mPFC        |          PCC          |
| :---------- | :--------------------: | --------------------: |
| Left        | `r searchSpace$L.mPFC` | `r searchSpace$L.PCC` |
| Right       | `r searchSpace$R.mPFC` | `r searchSpace$R.PCC` |
